Capturing Policies for BYOD

### 2016-11-28 paper.tex
added bit on proof graphs

Facts of the \emph{must}-kind represent obligations, actions that should be completed if a particular scenario presents itself.
For these facts we add a rule to ensure the obligation is performed.
This rule should be checked periodically to ensure compliance.
\begin{lstlisting}
$\langle\text{speaker}\rangle$ says $\langle\text{subject}\rangle$ hasSatisfiedObligation$\langle\text{Action}\rangle$
  if $\langle\text{subject}\rangle$ must$\langle\text{Action}\rangle$,
     $\langle\text{subject}\rangle$ has$\langle\text{Action}\rangle$.
\end{lstlisting}

@@

\subsection{Worked Examples}

@@

Once all the statements have been collected into an \emph{assertion context}.
Alice can use a SecPAL inference tool (such as AppPAL~\footnote{https://github.com/apppal/libapppal}) to check the policy has been satisfied.

\subsection{BYOD Idioms}
\todo{Describe common idioms and patterns found in each of the policies.  Check the earlier draft for some starting work}

\subsection{Delegation and Roles within Policies}

@@

Because \AppPAL's predicates have a predictible naming conventions (\autoref{ssec:changes}), our tooling can also generate additional rules to check if the acknowledgement has been made, and check whether there is anyone to acknowledge the policy. 
\begin{lstlisting}
'company' says E hasSatisfiedObligationToMustAcknowledged('policy')
  if E mustAcknowledged('policy').
     E hasAcknowledged('policy').
\end{lstlisting}

>>>>

Facts of the \emph{must}-kind represent obligations, actions that should be completed if a particular scenario presents itself.
For these facts we add a rule to ensure the obligation is performed.
This rule should be checked periodically to ensure compliance.
Our implementation contains tooling to generate these rules automatically.
\begin{lstlisting}
$\langle\text{speaker}\rangle$ says $\langle\text{subject}\rangle$ hasSatisfiedObligation$\langle\text{Action}\rangle$
  if $\langle\text{subject}\rangle$ must$\langle\text{Action}\rangle$,
     $\langle\text{subject}\rangle$ has$\langle\text{Action}\rangle$.
\end{lstlisting}

@@

\subsection{Worked Example}

@@

Once all the statements have been collected into an \emph{assertion context}.
Alice can use a SecPAL inference tool (such as AppPAL\footnote{https://github.com/apppal/libapppal}) to check the policy has been satisfied.
As well as making the decision we can output a proof tree (such as \autoref{fig:proof}).

\begin{figure}\centering
  \includegraphics[width=\linewidth]{figures/proof.png}
  \caption{Proof tree for Alice installing her app.}
  \label{fig:proof}
\end{figure}

\subsection{BYOD Idioms}

\subsubsection{Delegation and Roles within Policies}

@@
